---
title: "AMT Data Split"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
```

Load holistic score tibble from RData. Tidy data by rename and convert scores from chr to numeric 

```{r load}
load('amt_hs.RData')

# a function to split vid into turk and item
obt_turk <- function(x){
  vid_pt <- "(t\\d+)_(v\\d+)"
  tks <- str_match(x, vid_pt)
  tks[2] # turk

}

amt_hs <- holistic %>%
  rename(r_ch=catherinehutches) %>%
  rename(r_db=debradodd) %>%
  rename(r_lb=laurenbell16) %>%
  rename(r_nm=nicolemay) %>%
  rename(r_sj=sosnajoseph) %>%
  mutate(vid = unlist(vid)) %>%
  mutate(r_ch = as.numeric(r_ch)) %>%
  mutate(r_db = as.numeric(r_db)) %>%
  mutate(r_lb = as.numeric(r_lb)) %>%
  mutate(r_nm = as.numeric(r_nm)) %>%
  mutate(r_sj = as.numeric(r_sj)) 
```

Compute row mean from 5 individual raters' scores. Also, parse vid to obtain turk ID

```{r}
amt_hs <- amt_hs %>%
  mutate(final = rowMeans(select(., starts_with("r_")), na.rm = T))%>%
  select(vid, final) %>%
  mutate(turk = lapply(vid, obt_turk)) %>%
  mutate(turk = unlist(turk))

head(amt_hs)

```

Compute turk level mean of final scores.
```{r per_turk}
turk_hs <- amt_hs %>%
  group_by(turk) %>% 
  summarise(cnt = n(), turk_mean = mean(final)) %>%
  filter(cnt > 5)  # remove turks with only a few responses.

summary(turk_hs$turk_mean)

plot <- ggplot(turk_hs, aes(turk_mean)) +
  geom_histogram()

show(plot)
```

Sample turk_hs to split entire data into train and test.
```{r sample, message=FALSE, warning=FALSE}
require(caret)
intrain<-createDataPartition(y=turk_hs$turk_mean, p=0.8, list=FALSE)
train<-turk_hs[intrain,]
test <-turk_hs[-intrain,]

summary(test$turk_mean)
plot <- ggplot(test, aes(turk_mean)) +
  geom_histogram()

show(plot)
```

Based on turk split plan, generate response level train and test list files. Need check ASR outputs (ibm_asr.lst) since several responses cannot be recognized.

```{r response_list}
# a function to split ASR file name into id and turk
obt_id <- function(x){
  vid_pt <- "SELTCAWRS_(t\\d+_v\\d+)\\.md"
  tks <- str_match(x, vid_pt)
  tks[2] # id

}

asr <- read.table('ibm_asr.lst') %>%
  mutate(vid = lapply(V1, obt_id))

# merge asr w/ amt_hs
amt_hs_asr <- merge(amt_hs, asr, by="vid")

resp_train_lst <- amt_hs_asr %>%
  filter(turk %in% train$turk)
resp_test_lst <- amt_hs_asr %>%
  filter(turk %in% test$turk)

# a function to save vid and final score 
save_lst <- function(tbl, csvFile){
  out <- tbl %>%
    select(vid, final) %>%
    mutate(vid = paste0("SELTCAWRS_", vid))
  write.csv(out, file=csvFile, row.names = F)
}

save_lst(resp_train_lst, "amt2016_train.lst")
save_lst(resp_test_lst,  "amt2016_test.lst")
```