---
title: "Rating quality analysis"
output: html_notebook
---
```{r}
library(tidyverse)
library(magrittr)
library(irr)
```

Note that we used the following parameters when computing Intra-Class Correlation (ICC).
```{r}
my.icc <- function(mx){
  icc <- icc(mx, model="twoway", type="consistency", unit="average")
  icc$value
  
}

cor.min <- function(mx){
  mean_col <- rowMeans(mx, na.rm = T)
  cors <- cor(mx, y=mean_col, use = "complete.obs")
  min(cors)
  
}
cor.max <- function(mx){
  mean_col <- rowMeans(mx, na.rm = T)
  cors <- cor(mx, y=mean_col, use = "complete.obs")
  max(cors)
  
}
cor.ave <- function(mx){
  mean_col <- rowMeans(mx, na.rm = T)
  cors <- cor(mx, y=mean_col, use = "complete.obs")
  mean(cors)
  
}


```

On AMT video data set, compute ICC and meancor among holistic ratings (n=5)

```{r, echo=FALSE, eval=T, results='asis'}
obt_irr <- function(x){
  out <- x %>%
    na.omit() %>%
    select(catherinehutches:sosnajoseph) %>%
    mutate_each(funs(as.numeric)) %>%
    summarise(
    icc = my.icc(
    cbind(
    catherinehutches,
    debradodd,
    laurenbell16,
    nicolemay,
    sosnajoseph
    )
    ),
    r_min = cor.min(
    cbind(
    catherinehutches,
    debradodd,
    laurenbell16,
    nicolemay,
    sosnajoseph
    )
    ),
    r_max = cor.max(
    cbind(
    catherinehutches,
    debradodd,
    laurenbell16,
    nicolemay,
    sosnajoseph
    )
    ),
    r_ave = cor.ave(
    cbind(
    catherinehutches,
    debradodd,
    laurenbell16,
    nicolemay,
    sosnajoseph
    )
    )
   )
  out
  
}
```

Holistic

4/29 Note, following following running order
- data_reader.Rmd to load data
- data_split.Rmd to filter responses that cannot be recognized and with
  human rating issue. obtain resp_train_lst and resp_test_lst
- for each rating df, ONLY pick responses in (resp_train|test_lst)

```{r, echo=FALSE, eval=T, results='asis'}
to_use = rbind(resp_train_lst, resp_test_lst)$vid

in_expm <- function(x){
  x_in_expm <- x %>%
  mutate(vid = unlist(vid)) %>%
  mutate(in_expm = vid %in% to_use) %>%
  filter(in_expm == T)
  show(dim(x_in_expm))
  x_in_expm

}
obt_irr(in_expm(holistic))
```

Personality Traits:
```{r, echo=FALSE, eval=T, results='asis'}
obt_irr(in_expm(agreeable))
obt_irr(in_expm(extraversion))
obt_irr(in_expm(consci))
obt_irr(in_expm(emstability))
obt_irr(in_expm(openess))
```